\vspace{8pt} % Gap between title and text

\subsubsection{University of Pennsylvania, Research Assistant, Sep 2011 - Present}
\begin{itemize}
\item {\bf Distributed Provenance Compression} \hfill Sep 2015 -- Jun
  2016\\ Designed and implemented a framework for compressing network
  provenance in a distributed fashion. The framework places provenance
  trees into different equivalence classes, and stores only one
  concrete copy for provenance trees in the same equivalence class. To
  efficiently identify the equivalence class to which each provenance tree
  belongs, we performed static analysis on provenance maintenance
  sourcecode, and used the analysis results to compress provenance
  trees at runtime.


(in collaboration with Prof. Boon Thau Loo, Prof. Limin Jia and Prof. Wenchao Zhou)
\item {\bf Verification of Declarative Networking Programs} \hfill Jun
  2014 -- May 2015\\ Designed and implemented a framework for
  verifying safety properties of networking programs specified in
  declarative programming languages (e.g. NDLog). The declarative
  specification of networking applications is parsed and converted
  into dependency graph -- a data structure capturing the tuple-level
  dependency between relations in NDLog. To verify the safety
  properties -- which are specified in a restricted form of
  first-order logic -- we used the dependency graph to generate all
  candidate system execution traces, and ensure that the specified
  property holds on all traces. We developed a prototype to verify
  properties of SDN applications, and found several bugs in the
  applications.


(in collaboration with Prof. Boon Thau Loo, Prof. Limin Jia and Prof. Wenchao Zhou)
\item {\bf Program Logic for Secure Routing Protocols} \hfill Sep 2011
  -- May 2014\\ Developed a program logic for verifying security
  properties of secure routing protocols (e.g., Secure BGP). The logic
  is built on SANDlog, a variant specification language of Network
  Datalog (i.e., NDLog) with extension of security primitives, We used
  the logic to prove classical properties, such as path authenticity,
  of secure routing protocols. Our logic is proved to be sound with
  regards to the semantics of SANDlog.


(in collaboration with Prof. Boon Thau Loo, Prof. Limin Jia and Prof. Wenchao Zhou)
\end{itemize}
